Weight analysis

### 2022-11-20 code/cytokines/Cytokines_tissue_adjusted.Rmd
Progress

@@

#___Inspect tissue weight distribution____#
cytokines_long %>%       
  filter(exp_number == 3) %>% 
  kruskal_test(tissue_weight_mg ~ maternal_treatment) %>% 
  knitr::kable(escape = TRUE)

@@

#___Inspect tissue weight distribution____#
cytokines_long %>%       
  filter(exp_number == 4) %>% 
  kruskal_test(tissue_weight_mg ~ group) %>% 
  knitr::kable(escape = TRUE)

>>>>

# All experiments - tissue weight stats

```{r}

cytokines_long %>%       
  filter(exp_number %in% c("1","3")) %>% 
  group_by(exp_number) %>% 
  kruskal_test(tissue_weight_mg ~ type_of_feed)

#|exp_number |Effect       | DFn| DFd|       F|     p|p<.05 |   ges|
#|:----------|:------------|---:|---:|-------:|-----:|:-----|-----:|
#|1          |type_of_feed |   1| 298|   0.816| 0.367|      | 0.003|
#|3          |type_of_feed |   1| 378| 373.425| 0.000|*     | 0.497|
#|4          |type_of_feed |   1| 258|   9.863| 0.002|*     | 0.037|

@@

#___Inspect tissue weight distribution____#
cytokines_long %>%       
  filter(exp_number == 3) %>% 
  kruskal_test(tissue_weight_mg ~ type_of_feed)

@@

#___Inspect tissue weight distribution____#
cytokines_long %>%       
  filter(exp_number == 4) %>% 
  kruskal_test(tissue_weight_mg ~ type_of_feed)

cytokines_long %>%       
  filter(exp_number == 4) %>% 
  group_by(type_of_feed) %>% 
  summarize(mean = mean(tissue_weight_mg),
            sd = sd(tissue_weight_mg),
            median = median(tissue_weight_mg),
            iqr = IQR(tissue_weight_mg))

  anova_test(tissue_weight_mg ~ type_of_feed)

cytokines_long %>%       
  filter(exp_number == 4) %>% 
  anova_test(tissue_weight_mg ~ type_of_feed)

### 2022-11-20 code/weight_analysis.Rmd
Progress

@@

```{r style baseline bodyweight}
get_box_stats <- function(y, upper_limit = max(data$Bodyweight[data$Time == "Day2"]) * 1.0) {
  return(data.frame(
    y = 0.9 * upper_limit,
    label = paste(
      "n =", length(y), "\n",
      "Mean =", round(mean(y), 2), "\n" #,
      #"Median =", round(median(y), 2), "\n"
    )
  ))
}

my_comparisons <- list( c("Water", "AB"))

data %>% 
  filter(Time == "Day2") %>% 
  ggplot(aes(
    received_antibiotic, Bodyweight
  )) + 
  geom_boxplot() +
  facet_wrap(~experiment_no, 
             nrow = 1) + 
  geom_dotplot(
     binaxis = "y", stackdir = "center", dotsize = 0.5) + 
  stat_summary(
    fun.data = get_box_stats, geom = "text", hjust = 0.5, vjust = 0.9) +
  labs(
    title = "Body weight of offspring from antibiotic-treated vs water-treated mice",
    subtitle = "Results shown from each of the 4 experimental rounds",
    caption = "In Exp. 4 all mice received antibiotoics, hence no control.
    Comparison method: Student T-test",
    x = "Maternal Treatment",
    y = "Bodyweight at end of study (g)"
  ) +
  theme_bw() + 
  stat_compare_means(
    method = "t.test", 
    label.y = 3, 
    comparisons = my_comparisons
    )
```

@@

bodyweight_gain_BFvsFORM <- data %>% 
  mutate(weightgain = weight_end - weight_baseline) %>% 
  ggplot(aes(
    type_of_feed, weightgain
  )) + 
  geom_boxplot() +
  facet_wrap(~experiment_no, 
             nrow = 1) +
geom_dotplot(
     binaxis = "y", stackdir = "center", dotsize = 0.5) + 
  stat_summary(
    fun.data = get_box_stats, geom = "text", hjust = 0.2, vjust = 0.9) +
  labs(
    title = "Effect of Formula vs. Breastfeeding on Weight Gain",
    subtitle = "Results shown from each of the 4 experimental rounds",
    caption = "In Exp. 2 all mice were breastfed.
    Comparison method: Student T-test",
    x = "Type of feed",
    y = "Body weight increase  (g)"
  ) +
  theme_bw() + 
  stat_compare_means(
    method = "t.test", 
    label.y = 3, 
    comparisons = my_comparisons_2
    )
my_comparisons_2 <- list( c("Breastmilk", "Formula"))
bodyweight_gain_BFvsFORM
```

>>>>

## Weight at allocation - mat vs con
```{r weight-at-allocation-mat-vs-con}
get_box_stats <- function(y, upper_limit = max(data$bodyweight[data$time == "day_5"]) * 1.2) {
  return(data.frame(
    y =  0.9*upper_limit,
    label = paste(
      "n =", length(y), "\n",
      "Mean =", round(mean(y), 2), "\n" #,
      #"Median =", round(median(y), 2), "\n"
    )
  ))
}

my_comparisons <- list( c("CON", "MAT"))

data %>% 
  #filter(exp_number %in% c("1", "2", "3","4")) %>% 
  filter(time %in% c("day_3")) %>%
  drop_na(bodyweight) %>% 
  ggplot(
    aes(x = received_antibiotics,
        y = bodyweight)
  ) +
  geom_boxplot() +
  geom_dotplot(
     binaxis = "y", stackdir = "center", dotsize = 0.5) +
  facet_grid(~ exp_number) +
  stat_summary(
    fun.data = get_box_stats, geom = "text", hjust = 0.5, vjust = 0.9) +
  labs(
    #title = "Body weight of offspring from antibiotic-treated vs water-treated mice",
   # subtitle = "Results shown from each of the 4 experimental rounds",
    caption = "In Exp. 4 all mice received antibiotoics, hence no control.
    Comparison method: Student T-test",
    x = "Maternal Treatment",
    y = "Bodyweight at end of study (g)"
  ) +
  theme_bw() + 
  stat_compare_means(
    method = "t.test", 
    label.y = 3, 
    comparisons = my_comparisons
    )
```

## Weight at allocation - form vs BF
```{r weight-at-allocation-ff-vs-bf}
get_box_stats <- function(y, upper_limit = max(data$bodyweight[data$time == "day_5"]) * 1.2) {
  return(data.frame(
    y =  0.9*upper_limit,
    label = paste(
      "n =", length(y), "\n",
      "Mean =", round(mean(y), 2), "\n" #,
      #"Median =", round(median(y), 2), "\n"
    )
  ))
}

my_comparisons <- list( c("BF", "FF"))

data %>% 
  #filter(exp_number %in% c("1", "2", "3","4")) %>% 
  filter(time %in% c("day_5")) %>%
  drop_na(bodyweight) %>% 
  ggplot(
    aes(x = type_of_feed,
        y = bodyweight)
  ) +
  geom_boxplot() +
  geom_dotplot(
     binaxis = "y", stackdir = "center", dotsize = 0.5) +
  facet_grid(~ exp_number) +
  stat_summary(
    fun.data = get_box_stats, geom = "text", hjust = 0.5, vjust = 0.9) +
  labs(
    #title = "Body weight of offspring from antibiotic-treated vs water-treated mice",
   # subtitle = "Results shown from each of the 4 experimental rounds",
    caption = " Comparison method: Student T-test",
    x = "Type of feed",
    y = "Bodyweight at end of study (g)"
  ) +
  theme_bw() + 
  stat_compare_means(
    method = "t.test", 
    label.y = 4.35, 
    comparisons = my_comparisons
    )
```

@@

```{r style baseline bodyweight}
get_box_stats <- function(y, upper_limit = max(data$bodyweight[data$time == "day_5"]) * 1.0) {
  return(data.frame(
    y = 0.9 * upper_limit,
    label = paste(
      "n =", length(y), "\n",
      "Mean =", round(mean(y), 2), "\n" #,
      #"Median =", round(median(y), 2), "\n"
    )
  ))
}

my_comparisons <- list( c("CON", "MAT"))

data %>% 
  filter(time %in% c("day_3", "day_5")) %>% 
  ggplot(aes(
    time, bodyweight
  )) + 
  geom_boxplot() +
  facet_wrap(~ exp_number, 
             nrow = 1) + 
  geom_dotplot(
     binaxis = "y", stackdir = "center", dotsize = 0.5) + 
  stat_summary(
    fun.data = get_box_stats, geom = "text", hjust = 0.5, vjust = 0.9) +
  labs(
    title = "Body weight of offspring from antibiotic-treated vs water-treated mice",
    subtitle = "Results shown from each of the 4 experimental rounds",
    caption = "In Exp. 4 all mice received antibiotoics, hence no control.
    Comparison method: Student T-test",
    x = "Maternal Treatment",
    y = "Bodyweight at end of study (g)"
  ) +
  theme_bw() + 
  stat_compare_means(
    method = "t.test", 
    label.y = 3, 
    comparisons = my_comparisons
    )
```

@@

bodyweight_gain_BFvsFORM <- data %>% 
  mutate(weightgain = weight_end - weight_baseline) %>% 
  ggplot(aes(
    type_of_feed, weightgain
  )) + 
  geom_boxplot() +
  facet_wrap(~exp_number, 
             nrow = 1) +
geom_dotplot(
     binaxis = "y", stackdir = "center", dotsize = 0.5) + 
  stat_summary(
    fun.data = get_box_stats, geom = "text", hjust = 0.2, vjust = 0.9) +
  labs(
    title = "Effect of Formula vs. Breastfeeding on Weight Gain",
    subtitle = "Results shown from each of the 4 experimental rounds",
    caption = "In Exp. 2 all mice were breastfed.
    Comparison method: Student T-test",
    x = "Type of feed",
    y = "Body weight increase  (g)"
  ) +
  theme_bw() + 
  stat_compare_means(
    method = "t.test", 
    label.y = 3, 
    comparisons = my_comparisons_2
    )
my_comparisons_2 <- list( c("Breastmilk", "Formula"))
bodyweight_gain_BFvsFORM
```
